Quantifying uncertainty in Pareto estimates of global lake area

### 2023-02-06 manuscript/manuscript.tex
typo fix

\begin{figure}
	\centering
	\includegraphics{figures/predict_censor-1}
	\caption{Simulated lake area (purple line) where the portion calculated from the edf (>= 0.1 $km^2$) is denoted by a solid line and the portion calculated from the transformed cdf (< 0.1 $km^2$) is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (solid yellow line) is also shown.}
	\label{fig:predict_censor}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics{figures/predict_censor-1}
	\caption{Simulated lake area (yellow line) where the portion calculated from the edf (>= 0.1 $km^2$) is denoted by a solid line and the portion calculated from the transformed cdf (< 0.1 $km^2$) is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (solid purple line) is also shown.}
	\label{fig:predict_censor}
\end{figure}
